BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-06 tex/3-algorithms.tex
End of eval + conclusion future works.

% html extraction is not trival
Extracting metadata and content from html documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how html documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}. More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside html documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages \cite{brianwilson2008}, and more than 95\% of pages do not pass html validation \cite{brianwilson2008-a}. Under such circumstances, relying on html structure to extract content from web pages is not viable and other techniques need to be employed.

@@

% per blog procedure, related work
To extract content from blog posts, we procede by building extraction rules from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML page and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.

@@

% textual pseudocode
\autoref{extractionAlgo} shows the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}. The rule which is most frequently a \emph{best rule} is then returned.

@@

% embarrassingly parallel
One might notice that each \emph{best rule} computation is independent and operates on a different input pairs. This implies that \autoref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.

@@

% into: algo 1 defined
With functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) defined, the definition of \autoref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

@@

% proof
With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortised} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

@@

% authors
The case of authors is problematic because authors' names often appears in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score. The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

@@

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity. While scoring rules for comments extraction requires a more expensive algorithm, the proportion of candidates left after filter out rules with an insufficient number of results is very low in practice. Analog reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

>>>>

% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}. More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building extraction rules from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML page and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.

@@

% textual pseudocode
\autoref{extractionAlgo} shows the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute, out of all possible extraction rules, the best one with respect to a certain \code{ScoreFunction}. The rule which is most frequently a \emph{best rule} is then returned.

@@

% embarrassingly parallel
One might notice that each \emph{best rule} computation is independent and operates on a different input pair. This implies that \autoref{extractionAlgo} is \emph{embarrassingly parallel}: iterations of the outer loop can trivially be executed on multiple threads.

@@

% into: algo 1 defined
The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as the \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

@@

% proof
With bigrams computed in this dynamic programming manner, the total time needed to compute all \coderef{bigramsAlgo}\code{(}\emph{node.text}\code{)} is linear. To conclude the proof that \autoref{linearAlgo} runs in linear time we show that all other computations of the inner loop can be done in constant \emph{amortized} time. As the number of edges in a tree is one less than the number of nodes, the \emph{amortized} number of bigrams unions per inner loop iteration tends to one. Each \emph{quotient of similarity} computation requires one bigrams intersection and three bigrams length computations. Over a finite alphabet (we used printable ASCII), bigrams sizes have bounded size and each of these operations takes constant time.

@@

% authors
The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score. The heuristic we use to get around this issue consists in adding a new component in the \code{ScoreFunction} for authors extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

@@

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affects the asymptotic computational complexity. Scoring rules for comments extraction requires a more expensive algorithm. However, this is compensated by the fact that the proportion of candidates left, after filter out rules not returning enough results, is very low in practice. Analog reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

### 2013-12-06 tex/4-techniques.tex
up
End of eval + conclusion future works.

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. Finally we will talk about deployment to scalable, fault resilient distributed architecture.

@@

Our crawler is built on top of Scrapy \cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modular architecture illustrated in Figure~\ref{architecture}. Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

>>>>

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Finally we will talk about the design choices we made in view of large scale deployment.

@@

Our crawler is built on top of Scrapy \cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modular architecture illustrated in \autoref{architecture}. Several components can be plugged in Scrapy core infrastructure: \emph{Spiders}, \emph{Item Pipelines}, \emph{Downloader Middlewares} and \emph{Spider Middlewares}; each allowing to implement a different type of functionalities.

### 2013-12-06 tex/6-conclusion-and-future-work.tex
End of eval + conclusion future works.

\section{Conclusion and Future Work}
% What we presented, what we solved
In this paper, we presented the internals of the BlogForever web crawler. Its central article extraction procedure based on extraction rules generation was introduced along with theoretical and empirical evidences validating the approach. Simple adaptation of this procedure allowed to extract different types of contents, including authors, dates and comments. In order to support

blogs with JavaScript generated content

We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.

% Future work

Plan:
\begin{enumerate}
  \item Recap the problem and the objective
  \item Summarize how've solved it
  \item Mention challenges and problems
  \item Hint for future work
\end{enumerate}

Content:
\begin{enumerate}
  \item Web pages dynamically generated after filling a web form/doing some user action. This is not automated atm.
  \item Spacial reasoning (we already have the page rendered w PhantomJS)
  \item Low level PhantomJS hooks
  \item Tree edit distance matching
\end{enumerate}

>>>>

\section{Conclusion and Future Work}
% What we presented, what we solved
In this paper, we presented the internals of the BlogForever web crawler. Its central article extraction procedure based on extraction rules generation was introduced along with theoretical and empirical evidences validating the approach. Simple adaptation of this procedure allowed to extract different types of contents, including authors, dates and comments. In order to support rapidly evolving web technologies such as JavaScript generated content, the crawler uses a web browser to render pages before processing. We also discussed the overall software architecture, highlighting the design choices made to achieve both modularity and scalability.

% Future work, hybrid algos
Future work could investigate \emph{hybrid} extraction algorithms to try to achieve near 100\% success rates. Even if overall our approach obtains better performs, there are few cases where other techniques managed to extract data where we did not. This suggests that combining our approach with others such such as word density, tree edit distance matching or even spacial reasoning could lead to better performances.

% Deployment on a distributed architecture  
Another possible research direction would be the deployment of the BlogForever crawler on a large scale distributed system. This is particularly relevant in the domain of web crawling given that intensive network operations can be a serious bottleneck which benefits from the use of multiple Internet access points. We intend to explore this opportunities in our future work.

% Low level PhantomJS hooks
% I guess two future works is enough...

% Conclude the conclude
To open up further possibilities, the crawler presented in this paper is available under the MIT license from the project's website. \TODO{cite \\https://github.com/OlivierBlanvillain/blogforever-crawler or http://blogforever.eu/ ?}.
